An equivalence of compositional frameworks

### 2019-05-14 EquivCompFrameworks_20180911kc.tex
actually completed the double mapping

\begin{itemize}
\item {\chris Discuss the name of Decorated and Structured cospan double categories one last time? :)}
\item {\chris Where should we put some standard things we use? For exampe, lax monoidal pseudofunctor should be recalled early. Together with pseudonatural transformations I believe. For now, I put them in an unnamed section}
\item {\chris Notation between \cref{Equiv} and \cref{thm:decoratedcospans} right now does not match! Need to fix.}
%\item {\chris There might be a way to completely hide the details of version 'fibres have, reindexing preserve' if that's what we want to do.}
\end{itemize}

@@

\begin{thm}\label{SC}
Given a category $\mathsf{X}$ with finite colimits and a category $\mathsf{A}$ with finite coproducts and a finite coproduct preserving functor $L \colon \mathsf{A} \to \mathsf{X}$ with $\mathsf{A}$ and $\mathsf{X}$ regarded as cocartesian monoidal categories, there exists a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ which has:
\begin{enumerate}
\item{objects given by objects of $\mathsf{A}$,}
\item{vertical 1-morphisms given by morphisms of $\mathsf{A}$,}
\item{horizontal 1-cells given by cospans of $\mathsf{X}$ of the form:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c)$};
\node (B) at (1,0) {$x$};
\node (C) at (2,0) {$L(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$$} (B)
(C) edge node[above]{$$} (B);
\end{tikzpicture}
\]
and}
\item{2-morphisms given by maps of cospans of $\mathsf{X}$ of the form:
\begin{equation}\label{eq:2cellsStrCsp}
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,0) {$x$};
\node (C) at (2,0) {$L(c_2)$};
\node (A') at (0,-1) {$L(c_1^\prime)$};
\node (B') at (1,-1) {$x^\prime$};
\node (C') at (2,-1) {$L(c_2^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$$} (B)
(C) edge node[above]{$$} (B)
(A') edge node[above]{$$} (B')
(C') edge node[above]{$$} (B')
(A) edge node [left]{$L(f)$} (A')
(B) edge node [left]{$\alpha$} (B')
(C) edge node [left]{$L(g)$} (C');
\end{tikzpicture}
\end{equation}
Composition of horizontal 1-cells and 2-morphisms is given by pushouts in $\mathsf{X}$ and tensoring of objects is under binary coproducts in $\mathsf{A}$.
}
\end{enumerate}
\end{thm}
\begin{proof}
See the first two authors' work on structured cospans \cite{BC2}.
\end{proof}
{\chris Below, I commented out a nice short recalled version of decorated cospans, since now their definition is later. Use if we want to recall at some point later}
%In the previous section, we started with a symmetric lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$ and created a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
%\begin{enumerate}
%\item{objects of $\mathsf{A}$ as objects,}
%\item{morphisms of $\mathsf{A}$ as vertical 1-morphisms,}
%\item{horizontal 1-cells are given by $F$-decorated cospans, which are pairs:
%\[
%\begin{tikzpicture}[scale=1.5]
%\node (A) at (0,0) {$c_1$};
%\node (B) at (1,0) {$c$};
%\node (C) at (2,0) {$c_2$};
%\node (D) at (3,0) {$x \in F(c)$};
%\path[->,font=\scriptsize,>=angle 90]
%(A) edge node[above]{$i$} (B)
%(C) edge node[above]{$o$} (B);
%\end{tikzpicture}
%\]
%and}
%\item{2-morphisms are given by maps of cospans in $\mathsf{A}$:
%\[
%\begin{tikzpicture}[scale=1.5]
%\node (A) at (0,0) {$c_1$};
%\node (B) at (1,0) {$c$};
%\node (C) at (2,0) {$c_2$};
%\node (A') at (0,-1) {$c_1^\prime$};
%\node (B') at (1,-1) {$c^\prime$};
%\node (C') at (2,-1) {$c_2^\prime$};
%\node (D) at (3,0) {$x \in F(c)$};
%\node (D') at (3,-1) {$x^\prime \in F(c^\prime)$};
%\path[->,font=\scriptsize,>=angle 90]
%(A) edge node[above]{$i$} (B)
%(C) edge node[above]{$o$} (B)
%(A') edge node[above]{$i^\prime$} (B')
%(C') edge node[above]{$o^\prime$} (B')
%(A) edge node [left]{$f$} (A')
%(B) edge node [left]{$h$} (B')
%(C) edge node [left]{$g$} (C');
%\end{tikzpicture}
%\]
%together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
%\end{enumerate}

@@

Let $\OpFib(\A)$ denote the 2-subcategory of the slice 2-category $\mathbf{Cat}/ \A$ of opfibrations over $\A$, functors that preserve cocartesian liftings and natural transformations with vertical components. In fact, there is a 2-equivalence between opfibrations and pseudofunctors, see Section ?, induced by the so-called \emph{Grothendieck construction}.
%{\chris I don't mind this presentation of the Grothendieck construction which I admit not having seeing before. If we are to keep, we should put a reference. Otherwise we could stay more low level about this and just briefly describe what's going on.}
%\begin{defn}
%Let $\mathbf{Cat}_{\textnormal{lax},\star}$ denote the \define{2-category of lax-pointed categories} which has:
%\begin{enumerate}
%\item{objects as pairs $(\mathrm{A},c)$ where $\mathrm{A}$ is a category and $c$ is an object of $\mathrm{A}$, and}
%\item{a morphism from $(\mathrm{A},c)$ to $(\mathrm{X},y)$ is a pair $(F,f)$ where $F \colon \mathrm{A} \to \mathrm{X}$ is a functor and $f \colon F(c) \to y$ is a morphism in $\mathrm{X}$.}
%\end{enumerate}
%\end{defn}
%\begin{defn}
%Given a pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$, the \define{Grothendieck construction of} $F$ is given by the `strict 2-pullback' of the following cospan:
% \[
%\begin{tikzpicture}[scale=1.5]
%\node (D) at (1,1) {$\inta F$};
%\node (A) at (0,0) {$\mathrm{A}$};
%\node (B) at (1,-1) {$\mathbf{Cat}$};
%\node (C) at (2,0) {$\mathbf{Cat}_{\textnormal{lax},\star}$};
%\path[->,font=\scriptsize,>=angle 90]
%(D) edge[dashed] node[above]{$p$} (A)
%(D) edge[dashed] node[above]{$q$} (C)
%(A) edge node[below]{$F$} (B)
%(C) edge node[below]{$P$} (B);
%\end{tikzpicture}
%\]
%where $P \colon \mathbf{Cat}_{\textnormal{lax},\star} \to \mathbf{Cat}$ is the forgetful functor. 
\begin{defn}\label{def:GrothCat}
For any pseudofunctor $F\colon\A\to\bicat{Cat}$ where $\A$ is a category viewed as a 2-category with trivial 2-cells, the \textbf{Grothendieck category}
$\inta F$ has
\begin{itemize}
\item objects pairs $(a, x \in F(a))$ and
\item a morphism from $(a, x \in F(a))$ to $(b, y\in F(b))$ is a pair $(f \colon a \to b,\delta \colon F(f)(x) \to y)\in\A\times F(b)$.
\end{itemize}
This is an opfibred category over $\A$ via the obvious forgetful functor, with fibre categories $(\inta F)_a=F(a)$ and reindexing functors $f_!=F(f)$.
\end{defn}
%This can also be thought of as a morphism and a 2-morphism:
%\[
%\begin{tikzpicture}[scale=1.5]
%\node (A) at (0,0) {$\star$};
%\node (B) at (1,0.5) {$F(c)$};
%\node (C) at (1,-0.5) {$F(c^\prime)$};
%\node (D) at (2,0.5) {$c$};
%\node (E) at (2,-0.5) {$c^\prime$};
%\node (F) at (0.65,0) {$\Swarrow \alpha$};
%\path[->,font=\scriptsize,>=angle 90]
%(A) edge node[above]{$d$} (B)
%(B) edge node[right]{$F(f)$} (C)
%(A) edge node[below]{$d^\prime$} (C)
%(D) edge node[left] {$f$} (E);
%\end{tikzpicture}
%\]
The above in fact provides the one direction of the following well-known equivalence.
%gives rise to a 2-functor $[\A,\bicat{Cat}]_\pse\to \mathbf{Cat}/ \A$ which factors through the embedding $\OpFib(\A) \hookrightarrow \bicat{Cat} / \A$ as per the following theorem.
%: $$\inta F \colon [ \mathrm{A}, \mathbf{Cat} ] \to \textnormal{Opfib}(\mathrm{A}) \hookrightarrow \mathbf{Cat} / \mathrm{A}.$$

@@

\begin{proof}\emph{(Sketch)}
 The left adjoint $L\colon\A\to\X$ maps an object $a$ to the initial object in its fibre $\X_a$, denoted by $\bot_a$. By construction, $U(L(a))=U(\bot_a)=a$.
\end{proof}

@@

Using this functor $L_F$ between finitely cocomplete categories that preserves all colimits that exist (as a left adjoint), we can construct the double category of structured cospans $\scsp{L_F}{\inta F}$. Its objects and vertical morphisms are again those of the category $\A$, whereas horizontal 1-cells $a\tickar b$ are now cospans of the form $\cspn{L_F(a)}{v}{L_F(b)}{}{}$ in the Grothendieck category $\inta F$, which consist of two pairs of morphisms 
\begin{equation}\label{eq:scsphor1cell}
 (a,\bot_a)\xrightarrow{\scalebox{0.7}{$\begin{cases}i\colon a\to c &\textrm{in }\A \\!\colon F(i)(\bot_a)\to x &\textrm{in }F(c)\end{cases}$}}(c,x)\xleftarrow{\scalebox{0.7}{$\begin{cases}o\colon b\to c &\textrm{in }\A \\!\colon F(o)(\bot_b)\to x &\textrm{in }F(c)\end{cases}$}}(b,\bot_b)
\end{equation}
according to \cref{def:GrothCat}. The 2-morphisms in this double category are as in \cref{eq:2cellsStrCsp}. {\chris will expand.}

In order to prove that there is a double equivalence (\cref{ShulDubEquiv}) between $\dcsp{F}$ and $\scsp{L_F}{\inta F}$, we define a %n identity-on-objects and vertical morphism
double functor
\begin{displaymath}
\mathbb{E}\colon\scsp{L_F}{\inta F} \longrightarrow\dcsp{F}
\end{displaymath}
as follows. The object component of $\mathbb{E}=(\mathbb{E}_0,\mathbb{E}_1)$ is $\mathbb{E}_0 = \id_{\mathsf{A}}$ since both double categories have $\mathsf{A}$ as their vertical category; trivially, $\mathbb{E}_0$ is an equivalence of categories. Given a horizontal 1-cell in $\scsp{L_F}{\inta F}$ like \cref{eq:scsphor1cell}, the arrow component $\mathbb{E}_1$ of the double functor simply maps it to the decorated cospan
\begin{displaymath}
 a\xrightarrow{\; i \;}c\xleftarrow{\; o \;}b\;\textrm{ with decoration }x\in F(c)
\end{displaymath}
Notice that this really is a bijective correspondence since the unique maps from the initial objects in the fibres provide no extra information.

{\chris in progress}

>>>>

\begin{itemize}
\item {\chris Discuss notation for Decorated and Structured cospan double categories one last time? :)}
\item {\chris Where should we put some standard things we use? For exampe, lax monoidal pseudofunctor should be recalled early. Together with pseudonatural transformations I believe. For now, I put them in an unnamed section}
\item {\chris Notation between \cref{Equiv} and \cref{thm:decoratedcospans} right now does not match! Need to fix.}
%\item {\chris There might be a way to completely hide the details of version 'fibres have, reindexing preserve' if that's what we want to do.}
\end{itemize}

@@

\begin{thm}\label{SC}
Given a category $\mathsf{X}$ with finite colimits and a category $\mathsf{A}$ with finite coproducts and a finite coproduct preserving functor $L \colon \mathsf{A} \to \mathsf{X}$ with $\mathsf{A}$ and $\mathsf{X}$ regarded as cocartesian monoidal categories, there exists a symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ which has:
\begin{enumerate}
\item{objects given by objects of $\mathsf{A}$,}
\item{vertical 1-morphisms given by morphisms of $\mathsf{A}$,}
\item{horizontal 1-cells given by cospans of $\mathsf{X}$ of the form:
\begin{equation}\label{eq:structuredcospan}
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c)$};
\node (B) at (1,0) {$x$};
\node (C) at (2,0) {$L(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$$} (B)
(C) edge node[above]{$$} (B);
\end{tikzpicture}
\end{equation}
and}
\item{2-morphisms given by maps of cospans of $\mathsf{X}$ of the form:
\begin{equation}\label{eq:2cellsStrCsp}
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,0) {$x$};
\node (C) at (2,0) {$L(c_2)$};
\node (A') at (0,-1) {$L(c_1^\prime)$};
\node (B') at (1,-1) {$x^\prime$};
\node (C') at (2,-1) {$L(c_2^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$$} (B)
(C) edge node[above]{$$} (B)
(A') edge node[above]{$$} (B')
(C') edge node[above]{$$} (B')
(A) edge node [left]{$L(f)$} (A')
(B) edge node [left]{$\alpha$} (B')
(C) edge node [left]{$L(g)$} (C');
\end{tikzpicture}
\end{equation}
Composition of horizontal 1-cells and 2-morphisms is given by pushouts in $\mathsf{X}$ and tensoring of objects is under binary coproducts in $\mathsf{A}$.
}
\end{enumerate}
\end{thm}
\begin{proof}
See the first two authors' work on structured cospans \cite{BC2}.
\end{proof}
{\chris Below, I commented out a nice short recalled version of decorated cospans, since now their definition is later. Use if we want to recall at some point later}
%In the previous section, we started with a symmetric lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$ and created a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ which has:
%\begin{enumerate}
%\item{objects of $\mathsf{A}$ as objects,}
%\item{morphisms of $\mathsf{A}$ as vertical 1-morphisms,}
%\item{horizontal 1-cells are given by $F$-decorated cospans, which are pairs:
%\[
%\begin{tikzpicture}[scale=1.5]
%\node (A) at (0,0) {$c_1$};
%\node (B) at (1,0) {$c$};
%\node (C) at (2,0) {$c_2$};
%\node (D) at (3,0) {$x \in F(c)$};
%\path[->,font=\scriptsize,>=angle 90]
%(A) edge node[above]{$i$} (B)
%(C) edge node[above]{$o$} (B);
%\end{tikzpicture}
%\]
%and}
%\item{2-morphisms are given by maps of cospans in $\mathsf{A}$:
%\[
%\begin{tikzpicture}[scale=1.5]
%\node (A) at (0,0) {$c_1$};
%\node (B) at (1,0) {$c$};
%\node (C) at (2,0) {$c_2$};
%\node (A') at (0,-1) {$c_1^\prime$};
%\node (B') at (1,-1) {$c^\prime$};
%\node (C') at (2,-1) {$c_2^\prime$};
%\node (D) at (3,0) {$x \in F(c)$};
%\node (D') at (3,-1) {$x^\prime \in F(c^\prime)$};
%\path[->,font=\scriptsize,>=angle 90]
%(A) edge node[above]{$i$} (B)
%(C) edge node[above]{$o$} (B)
%(A') edge node[above]{$i^\prime$} (B')
%(C') edge node[above]{$o^\prime$} (B')
%(A) edge node [left]{$f$} (A')
%(B) edge node [left]{$h$} (B')
%(C) edge node [left]{$g$} (C');
%\end{tikzpicture}
%\]
%together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
%\end{enumerate}

@@

Let $\OpFib(\A)$ denote the 2-subcategory of the slice 2-category $\mathbf{Cat}/ \A$ of opfibrations over $\A$, functors that preserve cocartesian liftings and natural transformations with vertical components. In fact, there is a 2-equivalence between opfibrations and pseudofunctors, see Section ?, induced by the so-called \emph{Grothendieck construction}.
%{\chris I don't mind this presentation of the Grothendieck construction which I admit not having seeing before. If we are to keep, we should put a reference. Otherwise we could stay more low level about this and just briefly describe what's going on.}
%\begin{defn}
%Let $\mathbf{Cat}_{\textnormal{lax},\star}$ denote the \define{2-category of lax-pointed categories} which has:
%\begin{enumerate}
%\item{objects as pairs $(\mathrm{A},c)$ where $\mathrm{A}$ is a category and $c$ is an object of $\mathrm{A}$, and}
%\item{a morphism from $(\mathrm{A},c)$ to $(\mathrm{X},y)$ is a pair $(F,f)$ where $F \colon \mathrm{A} \to \mathrm{X}$ is a functor and $f \colon F(c) \to y$ is a morphism in $\mathrm{X}$.}
%\end{enumerate}
%\end{defn}
%\begin{defn}
%Given a pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$, the \define{Grothendieck construction of} $F$ is given by the `strict 2-pullback' of the following cospan:
% \[
%\begin{tikzpicture}[scale=1.5]
%\node (D) at (1,1) {$\inta F$};
%\node (A) at (0,0) {$\mathrm{A}$};
%\node (B) at (1,-1) {$\mathbf{Cat}$};
%\node (C) at (2,0) {$\mathbf{Cat}_{\textnormal{lax},\star}$};
%\path[->,font=\scriptsize,>=angle 90]
%(D) edge[dashed] node[above]{$p$} (A)
%(D) edge[dashed] node[above]{$q$} (C)
%(A) edge node[below]{$F$} (B)
%(C) edge node[below]{$P$} (B);
%\end{tikzpicture}
%\]
%where $P \colon \mathbf{Cat}_{\textnormal{lax},\star} \to \mathbf{Cat}$ is the forgetful functor. 
\begin{defn}\label{def:GrothCat}
For any pseudofunctor $F\colon\A\to\bicat{Cat}$ where $\A$ is a category viewed as a 2-category with trivial 2-cells, the \textbf{Grothendieck category}
$\inta F$ has
\begin{itemize}
\item objects pairs $(a, x \in F(a))$ and
\item a morphism from $(a, x \in F(a))$ to $(b, y\in F(b))$ is a pair $(f \colon a \to b,\delta \colon F(f)(x) \to y)\in\A\times F(b)$.
\end{itemize}
{\chris Might need to write the composition rule? Depending on the final proof of Big Theorem.}
This is an opfibred category over $\A$ via the obvious forgetful functor, with fibre categories $(\inta F)_a=F(a)$ and reindexing functors $f_!=F(f)$.
\end{defn}
%This can also be thought of as a morphism and a 2-morphism:
%\[
%\begin{tikzpicture}[scale=1.5]
%\node (A) at (0,0) {$\star$};
%\node (B) at (1,0.5) {$F(c)$};
%\node (C) at (1,-0.5) {$F(c^\prime)$};
%\node (D) at (2,0.5) {$c$};
%\node (E) at (2,-0.5) {$c^\prime$};
%\node (F) at (0.65,0) {$\Swarrow \alpha$};
%\path[->,font=\scriptsize,>=angle 90]
%(A) edge node[above]{$d$} (B)
%(B) edge node[right]{$F(f)$} (C)
%(A) edge node[below]{$d^\prime$} (C)
%(D) edge node[left] {$f$} (E);
%\end{tikzpicture}
%\]
The above in fact provides the one direction of the following well-known equivalence.
%gives rise to a 2-functor $[\A,\bicat{Cat}]_\pse\to \mathbf{Cat}/ \A$ which factors through the embedding $\OpFib(\A) \hookrightarrow \bicat{Cat} / \A$ as per the following theorem.
%: $$\inta F \colon [ \mathrm{A}, \mathbf{Cat} ] \to \textnormal{Opfib}(\mathrm{A}) \hookrightarrow \mathbf{Cat} / \mathrm{A}.$$

@@

\begin{proof}\emph{(Sketch)}
 The left adjoint $L\colon\A\to\X$ maps an object $a$ to the initial object in its fibre $\X_a$, denoted by $\bot_a$. By construction, $U(L(a))=U(\bot_a)=a$. On morphisms $f\colon a\to a'$, $L(f)$ is defined by
 \begin{equation}\label{eq:Lonarrows}
  \bot_a\xrightarrow{\Cocart(f,\bot_a)}f_!(\bot_a)\xrightarrow{\;\stackrel{\chi_a}{\cong}\;}\bot_{a'}
 \end{equation}
where $\chi_a$ is the unique isomorphism between the initial objects in the fibre above $a'$ since $f_!$ preserves them.
\end{proof}

@@

Using this functor $L_F$ between finitely cocomplete categories that preserves all colimits that exist (as a left adjoint), we can construct the double category of structured cospans $\scsp{L_F}{\inta F}$. Its objects and vertical morphisms are again those of the category $\A$, whereas horizontal 1-cells $a\tickar b$ as in \cref{eq:structuredcospan} are now cospans of the form $\cspn{L_F(a)}{v}{L_F(b)}{}{}$ in the Grothendieck category $\inta F$. Explicitly, they consist of two pairs of morphisms 
\begin{equation}\label{eq:scsphor1cell}
 (a,\bot_a)\xrightarrow{\scalebox{0.7}{$\begin{cases}i\colon a\to c &\textrm{in }\A \\!\colon F(i)(\bot_a)\to x &\textrm{in }F(c)\end{cases}$}}(c,x)\xleftarrow{\scalebox{0.7}{$\begin{cases}o\colon b\to c &\textrm{in }\A \\!\colon F(o)(\bot_b)\to x &\textrm{in }F(c)\end{cases}$}}(b,\bot_b)
\end{equation}
where $x\in F(c)$, according to \cref{def:GrothCat}. Finally, the 2-morphisms in this double category are as described in \cref{eq:2cellsStrCsp}, in this context fully unravelled below:
\begin{displaymath}
 \begin{tikzcd}[sep=1.5in,ampersand replacement=\&]
 (a,\bot_a)\ar[r,"{\begin{cases}i\colon a\to c &\textrm{in }\A \\!\colon F(i)(\bot_a)\to x &\textrm{in }F(c)\end{cases}}"]\ar[d,"{\begin{cases}f\colon a\to a' &\textrm{in }\A \\\chi_a\colon F(f)(\bot_a)\cong \bot_{a'} &\textrm{in }F(a')\end{cases}}"description] \& (c,x) \ar[d,"{\begin{cases}k\colon c\to c' &\textrm{in }\A \\h\colon F(k)(x)\to x' &\textrm{in }F(c')\end{cases}}"description] \& (b,\bot_b)\ar[l,"{\begin{cases}o\colon b\to c &\textrm{in }\A \\!\colon F(o)(\bot_b)\to x &\textrm{in }F(c)\end{cases}}"']\ar[d,"{\begin{cases}g\colon b\to b' &\textrm{in }\A \\\chi_b\colon F(g)(\bot_b)\cong \bot_{b'} &\textrm{in }F(b')\end{cases}}"description] \\
 (a',\bot_{a'})\ar[r,"{\begin{cases}i'\colon a'\to c' &\textrm{in }\A \\!\colon F(i')(\bot_{a'})\to x' &\textrm{in }F(c')\end{cases}}"'] \& (c',x') \& (b',\bot_{b'})\ar[l,"{\begin{cases}o'\colon b'\to c' &\textrm{in }\A \\!\colon F(o')(\bot_{b'})\to x' &\textrm{in }F(c')\end{cases}}"]
 \end{tikzcd}
\end{displaymath}
where the outside vertical legs come from the definition of $L_F$ on arrows, \cref{eq:Lonarrows}. 
{\chris The above diagram might be a bit overwhelming, but all info is there. Choose which parts are required for a smooth proof!}
The square commutativities translate to $k\circ i=i'\circ f$ and $k\circ o=o'\circ g$ in $\A$, and also by composition in the Grothendieck category, to
\begin{gather*}
 F(k\circ i)(\bot_a)\cong Fk(Fi(\bot_a))\xrightarrow{Fk(!)}Fk(x)\xrightarrow{h}x'= \\
 F(i'\circ f)(\bot_a)\cong Fi'(Ff(\bot_a))\xrightarrow{Fi'(\chi_a)}Fi'(\bot_{a'})\xrightarrow{!}x'
\end{gather*}
in the category $F(c')$. However, since all maps are unique in the above equality {\chris discuss with John and Kenny}, this gives no extra conditions for the morphisms involved, and similarly for the equality including $o, o'$.

In order to prove that there is a double equivalence (\cref{ShulDubEquiv}) between $\dcsp{F}$ and $\scsp{L_F}{\inta F}$, we define a %n identity-on-objects and vertical morphism
double functor
\begin{displaymath}
\mathbb{E}\colon\scsp{L_F}{\inta F} \longrightarrow\dcsp{F}
\end{displaymath}
as follows. The object component of $\mathbb{E}=(\mathbb{E}_0,\mathbb{E}_1)$ is $\mathbb{E}_0 = \id_{\mathsf{A}}$ since both double categories have $\mathsf{A}$ as their vertical category; trivially, $\mathbb{E}_0$ is an equivalence of categories. Given a horizontal 1-cell in $\scsp{L_F}{\inta F}$ like \cref{eq:scsphor1cell}, the arrow component $\mathbb{E}_1$ of the double functor simply maps it to the decorated cospan
\begin{displaymath}
 a\xrightarrow{\; i \;}c\xleftarrow{\; o \;}b\;\textrm{ with decoration }x\in F(c)
\end{displaymath}
Notice that this really is a bijective correspondence since the unique maps from the initial objects in the fibres provide no extra information. Finally, given a 2-morphism of $L_F$-structured cospans as described above, $\mathbb{E}_1$ maps it to the underlying cospan 2-morphism
\begin{displaymath}
 \begin{tikzcd}
a\ar[r,"i"]\ar[d,"f"'] & c\ar[d,"k"] & b\ar[l,"o"']\ar[d,"g"] \\
a'\ar[r,"i'"']& c' & b'\ar[l,"o'"]
 \end{tikzcd}
\end{displaymath}
 in $\A$ along with the map $h\colon Fk(x)\to x'$ in $F(c')$, namely a decorated cospan 2-morphism as per \cref{eq:FCsp2morph}.

{\chris Now the checking of the equivalence should follow! perhaps in less detail than currently?}
